---
title: Color Palettes in R
author: TF
date: '2018-07-22'
slug: color-palettes-in-r
categories: []
tags:
  - R
header:
  caption: ''
  image: ''
---

Colors. Finding the right ones to make a plot look good can be hard. I always like to use colors that really help set my plots apart. `tidyverse` and `ggplot` in particular are great at incorporating wonderful palettes. However, recently I was vexed by a plot where I couldnt just use a theme addition to add the colors I wanted and instead had to specify each color I wanted. At the time I wanted to use something from the `ggsci` package but coudlnt find the names or hex codes for the color. This post is meant to be a reference for myself and others on the different hex codes for packages.

#libraries
```{r include=TRUE, results='hide', message=FALSE, warning=FALSE}
library(tidyverse)
library(scales)
library(RColorBrewer)
library(ggsci)
library(wesanderson)
```

#ggsci colors and Hex (not a complete list)

JAMA
```{r message=FALSE, warning=FALSE}
show_col(pal_jama("default")(7))
```

NEJM
```{r message=FALSE, warning=FALSE}
show_col(pal_nejm("default")(7))
```

nature publishing group
```{r message=FALSE, warning=FALSE}
show_col(pal_npg("nrc")(10))
```

Univof Chicago
```{r message=FALSE, warning=FALSE}
show_col(pal_uchicago("default")(9))
    show_col(pal_uchicago("light")(9))
    show_col(pal_uchicago("dark")(9))
```

J of Clin Oncology
```{r message=FALSE, warning=FALSE}
show_col(pal_jco("default")(10))
```

Lancet
```{r message=FALSE, warning=FALSE}
show_col(pal_lancet("lanonc")(9))
```

Star Trek
```{r message=FALSE, warning=FALSE}
show_col(pal_startrek("uniform")(7))
```

Simpsons
```{r message=FALSE, warning=FALSE}
show_col(pal_simpsons("springfield")(16))
```

Rick and Morty
```{r message=FALSE, warning=FALSE}
show_col(pal_rickandmorty("schwifty")(12))
```

#Display overall Brewer colors
```{r include=TRUE, warning=FALSE}
display.brewer.all()
```
```{r include=TRUE, warning=FALSE}
brewer.pal.info
```

#Brewer Hex and Color palette
BrBG
can use:
```{r include=TRUE, warning=FALSE}
brewer.pal(n=11,name="BrBG")
```
```{r include=TRUE, warning=FALSE}
display.brewer.pal(n=11,name="BrBG")
```

or can use `show_col` command instead
```{r include=TRUE, warning=FALSE}
show_col(brewer_pal(palette = "BrBG")(11))
```

#Wes Anderson Movie Color Themes
```{r include=TRUE, warning=FALSE}
wes_palettes
```

Bottle Rocket 1
```{r include=TRUE, warning=FALSE}
show_col(wes_palettes$BottleRocket1)
```

Bottle Rocket 2
```{r include=TRUE, warning=FALSE}
show_col(wes_palettes$BottleRocket2)
```

Rushmore 1
```{r include=TRUE, warning=FALSE}
show_col(wes_palettes$Rushmore1)
```

Rushmore 2
```{r include=TRUE, warning=FALSE}
show_col(wes_palettes$Rushmore2)
```

Royal 1
```{r include=TRUE, warning=FALSE}
show_col(wes_palettes$Royal1)
```

Royal 2
```{r include=TRUE, warning=FALSE}
show_col(wes_palettes$Royal2)
```

Zissou1
```{r include=TRUE, warning=FALSE}
show_col(wes_palettes$Zissou1)
```

Darjeeling1
```{r include=TRUE, warning=FALSE}
show_col(wes_palettes$Darjeeling1)
```
Darjeeling2
```{r include=TRUE, warning=FALSE}
show_col(wes_palettes$Darjeeling2)
```

Fantastic Fox 1
```{r include=TRUE, warning=FALSE}
show_col(wes_palettes$FantasticFox1)
```

Moonrise1
```{r include=TRUE, warning=FALSE}
show_col(wes_palettes$Moonrise1)
```

Moonrise2
```{r include=TRUE, warning=FALSE}
show_col(wes_palettes$Moonrise2)
```

Moonrise3
```{r include=TRUE, warning=FALSE}
show_col(wes_palettes$Moonrise3)
```

GrandBudapest1
```{r include=TRUE, warning=FALSE}
show_col(wes_palettes$GrandBudapest1)
```

GrandBudapest2
```{r include=TRUE, warning=FALSE}
show_col(wes_palettes$GrandBudapest2)
```

IsleofDogs1
```{r include=TRUE, warning=FALSE}
show_col(wes_palettes$IsleofDogs1)
```

IsleofDogs2
```{r include=TRUE, warning=FALSE}
show_col(wes_palettes$IsleofDogs2)
```

#References:

https://rpubs.com/anhld/169514
https://www.nceas.ucsb.edu/~frazier/RSpatialGuides/colorPaletteCheatsheet.pdf
https://cran.r-project.org/web/packages/ggsci/ggsci.pdf
http://www.sthda.com/english/wiki/colors-in-r